---
title: "NetworkAnalysis_PositivePsychology"
author: "Hyein"
date: "2025-04-12"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Descriptive statistics

```{r}
#import dataset
library(readxl)
PPI_dataset <- read_excel("/Users/hyeinkim/Documents/N741/milestone/PPI_dataset.xlsx")


library(dplyr)
library(tidyr)

PPI_dataset %>%
  summarise(across(everything(), ~ mean(is.na(.) | . == -999) * 100)) %>%
  pivot_longer(cols = everything(),
               names_to = "Variable",
               values_to = "Missing_Percentage") %>%
  mutate(Missing_Percentage = round(Missing_Percentage, 2)) %>%
  arrange(desc(Missing_Percentage))


#missing data handling
# convert "-999" to NA in the dataset 
PPI_dataset[PPI_dataset == -999] <- NA

# remove row with NA 
PPI_dataset <- na.omit(PPI_dataset)
```

#name categorical variables

```{r}
PPI_dataset$Income <- factor(PPI_dataset$Income)
PPI_dataset$Sex <- factor(PPI_dataset$Sex)

PPI_dataset$Income <- factor(PPI_dataset$Income,
                             levels = c(1, 2, 3, 4, 5),
                             labels = c("<$9999",
                                        "$10,000–$29,999",
                                        "$30,000–$59,999",
                                        "$60,000–$89,999",
                                        ">$90,000"))

PPI_dataset$Sex <- factor(PPI_dataset$Sex,
                          levels = c(1, 2),
                          labels = c("Male", "Female"))
```



#Basic Descriptive Statistics, Table 1

```{r}
summary(PPI_dataset[, c("Flourish_PreTotal", "CESD_PreTotal", "AHS_PreTotal",
                 "BMPN_Sat_Aut_Pre","BMPN_Sat_Rel_Pre", "BMPN_Sat_Com_Pre",
                 "PANAS_Pos_Pre", "AGE", "Income", "Sex")])

#Mean and SD
library(table1)
table1(~Flourish_PreTotal+CESD_PreTotal+AHS_PreTotal+BMPN_Sat_Aut_Pre+BMPN_Sat_Rel_Pre+BMPN_Sat_Com_Pre+PANAS_Pos_Pre+AGE+Income+Sex, data=PPI_dataset) 
```


#Correlation among the psychological constructs


```{r}
library(dplyr)
cor_data <- PPI_dataset %>%
  select(Flourish_PreTotal, CESD_PreTotal, AHS_PreTotal, 
         BMPN_Sat_Aut_Pre, BMPN_Sat_Rel_Pre, BMPN_Sat_Com_Pre, PANAS_Pos_Pre)

cor_matrix <- cor(cor_data, use = "complete.obs", method = "pearson")
cor_matrix


library(corrr)
cor_data %>% 
  correlate() %>% 
  stretch() %>% 
  arrange(desc(r))



```

#Figure 1. Heatmap plot 
```{r}
library(ggcorrplot)
ggcorrplot(cor_matrix, 
           lab = TRUE, 
           type = "lower", 
           title = "Correlation Between Flourishing and Psychological Constructs")
```

Network analysis

**Select only PANAS_pro and Flourishing**
```{r}

library(bootnet)
library(qgraph)
library(dplyr)

#Preprocessing

#select PANAS_positive and Flourishing scale

network_data1 <- PPI_dataset[, c("PANAS_1", "PANAS_3", "PANAS_5", "PANAS_9", "PANAS_10", "PANAS_12", "PANAS_14", "PANAS_16", "PANAS_17", "PANAS_19","Flourish_1", "Flourish_2", "Flourish_3", "Flourish_4", "Flourish_5", "Flourish_6", "Flourish_7", "Flourish_8")]

network_data1 <-na.omit(network_data1)
network_data1 <- network_data1[, sapply(network_data1, function(x) sd(x, na.rm = TRUE) != 0)]

library(bootnet)
network_model1 <- estimateNetwork(network_data1,
                                  default = "EBICglasso",
                                  corMethod = "cor_auto")
plot(network_model1)

```

#flourishing and AHS (Adult Hope Scale)
```{r}

network_data2 <- PPI_dataset[, c("AHS_1", "AHS_2", "AHS_3", "AHS_4", "AHS_5", "AHS_6", "AHS_7", "AHS_8", "AHS_9",  "AHS_10", "AHS_11", "Flourish_1", "Flourish_2", "Flourish_3", "Flourish_4", "Flourish_5", "Flourish_6", "Flourish_7", "Flourish_8")]


network_data2 <-na.omit(network_data2)
network_data2 <- network_data2[, sapply(network_data2, function(x) sd(x, na.rm = TRUE) != 0)]

library(bootnet)
library(qgraph)
library(dplyr)

network_model2 <- estimateNetwork(network_data2,
                                  default = "EBICglasso",
                                  corMethod = "cor")
plot(network_model2)

```

"An empty network was selected to be the best fitting network."
--> What should I do to solve this problem? 


#CESD recoding evaluation
```{r}

# 1. select only necessary variables 
cesd_vars <- PPI_dataset %>%
  select(CESD_PreTotal, CESD_5, CESD_8)

# 2.correlation test 
cor.test(cesd_vars$CESD_5, cesd_vars$CESD_PreTotal)  # CESD_5 vs Total
cor.test(cesd_vars$CESD_8, cesd_vars$CESD_PreTotal)  # CESD_8 vs Total


# make new recoded variables 
cesd_vars <- cesd_vars %>%
  mutate(
    CESD_5_R = 3 - CESD_5,
    CESD_8_R = 3 - CESD_8
  )

# recheck the correlation
cor.test(cesd_vars$CESD_5_R, cesd_vars$CESD_PreTotal)
cor.test(cesd_vars$CESD_8_R, cesd_vars$CESD_PreTotal)

```


# Based on the correlation analyses, both CESD_5 and CESD_8 show strong positive correlations with the total CES-D score (CESD_PreTotal), while their reverse-coded versions (CESD_5_R and CESD_8_R) show strong negative correlations.
# This pattern indicates that the original CESD_5 and CESD_8 variables were already reverse-coded in the raw dataset. Applying reverse coding again (3 - x) in this case results in inverting the intended direction, leading to an incorrect interpretation.
# Therefore, reverse coding is not necessary, as the original variables are already in the correct (reverse-coded) format.



#flourishing and CESD (Depression)
```{r}
network_data3 <- PPI_dataset[, c("CESD_1", "CESD_2", "CESD_3", "CESD_4", "CESD_5", 
  "CESD_6", "CESD_7", "CESD_8", "CESD_9", "CESD_10", "Flourish_1", "Flourish_2", "Flourish_3", "Flourish_4", "Flourish_5", "Flourish_6", "Flourish_7", "Flourish_8")]


network_data3 <-na.omit(network_data3)
network_data3 <- network_data3[, sapply(network_data3, function(x) sd(x, na.rm = TRUE) != 0)]

library(bootnet)
library(qgraph)
library(dplyr)

network_model3 <- estimateNetwork(network_data3,
                                  default = "EBICglasso",
                                  corMethod = "cor_auto")
plot(network_model3)
```


#flourishing and Autonomy
```{r}


network_data4 <- PPI_dataset[, c("PsyNeed_1",  "PsyNeed_7", "PsyNeed_13", "PsyNeed_19", "Flourish_1", "Flourish_2", "Flourish_3", "Flourish_4", "Flourish_5", "Flourish_6", "Flourish_7", "Flourish_8")]


network_data4 <-na.omit(network_data4)
network_data4 <- network_data4[, sapply(network_data4, function(x) sd(x, na.rm = TRUE) != 0)]

library(bootnet)
library(qgraph)
library(dplyr)

network_model4 <- estimateNetwork(network_data4,
                                  default = "EBICglasso",
                                  corMethod = "cor_auto")
plot(network_model4)
```

#flourishing and Relatedness
```{r}
network_data5 <- PPI_dataset[, c("PsyNeed_3",  "PsyNeed_9", "PsyNeed_15", "PsyNeed_21", "Flourish_1", "Flourish_2", "Flourish_3", "Flourish_4", "Flourish_5", "Flourish_6", "Flourish_7", "Flourish_8")]

network_data5 <-na.omit(network_data5)
network_data5 <- network_data5[, sapply(network_data5, function(x) sd(x, na.rm = TRUE) != 0)]

library(bootnet)
library(qgraph)
library(dplyr)

network_model5 <- estimateNetwork(network_data5,
                                  default = "EBICglasso",
                                  corMethod = "cor_auto")
plot(network_model5)


```

#flourishing and Competence
```{r}
network_data6 <- PPI_dataset[, c("PsyNeed_5",  "PsyNeed_11", "PsyNeed_17", "PsyNeed_23", "Flourish_1", "Flourish_2", "Flourish_3", "Flourish_4", "Flourish_5", "Flourish_6", "Flourish_7", "Flourish_8")]


network_data6 <-na.omit(network_data6)
network_data6 <- network_data6[, sapply(network_data6, function(x) sd(x, na.rm = TRUE) != 0)]

library(bootnet)
library(qgraph)
library(dplyr)

network_model6 <- estimateNetwork(network_data6,
                                  default = "EBICglasso",
                                  corMethod = "cor_auto")
plot(network_model6)


```
